Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-09 paper/structureScene.tex
add section about pca

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization algorithm. Gaussian models are compared using Monte-Carlo sampling approaximation.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/overall}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$. \ml{add gmms}}
\label{fig:ASS_1}
\end{center}
\end{figure}

>>>>

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization (EM) algorithm. Gaussian models are compared using Monte-Carlo sampling approaximation. In order to ensure convergence of the EM algorithm when considering the scattering features as input, the dimension of the feature vector is reduced from 1367 to 30 by projecting the features over the 30 principal components computed over the whole dataset.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/overall}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}
